%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Walker Gollapudi} \\ \vspace{1pt}
    \small 317-764-8819 $|$ \href{mailto:wgollapudi@outlook.com}{\underline{wgollapudi@outlook.edu}} $|$ 
    \href{https://linkedin.com/in/wgollapudi}{\underline{linkedin.com/in/wgollapudi}} $|$
    \href{https://github.com/wgollapudi}{\underline{github.com/wgollapudi}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {Bachelor of Science in Computer Science \& Mathematics, Minor in Economics}{May 2027}
%  \resumeSubheading
%      {Park Tudor School}{Indianapolis, IN}
%      {Global Scholars Diploma}{Aug. 2019 -- May 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CS 240 Development Teaching Assistant}{Oct. 2024 -- Present}
      {Purdue University}{West Lafayette, IN}
      \resumeItemListStart
        \resumeItem{Collaborated with course leadership to design, write, and implement instructional materials for 700+ students.}
        \resumeItem{Authored and implemented homework assignments in LaTeX, developing program solutions and test modules in C.}
        \resumeItem{Optimized and managed Git-based assignment distribution and submission system as well as general course infrastructure, streamlining course operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Apprenticeship}{Oct. 2023 -- Dec. 2023}
      {Amazon Web Services - Amazon Open Source Contributor Initiative}{Virtual}
      \resumeItemListStart
        \resumeItem{Collaborated with AWS Principal Engineers on Amazon OpenSearch, contributing to the visualization dashboards through hands-on development and agile team practices.}
        \resumeItem{Delivered 100+ lines of code that were approved and deployed to production, strengthening OpenSearch’s capabilities as an open-source data search and visualization tool.}
        \resumeItem{Gained proficiency in Git and GitHub, while developing team collaboration skills through agile development cycles focused on iterative learning and software best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Research Intern}{July 2018 -- Aug. 2023}
      {NASA - Ames Research Center}{Mountain View, CA}
      \resumeItemListStart
        \resumeItem{Contributed to ExoMiner, a deep learning model developed to discover new exoplanets from Kepler and TESS data.}
        \resumeItem{Implemented specialized regularization techniques to mitigate overfitting, including Spatial Dropout and DropBlock.}
        \resumeItem{Integrated dropout-based uncertainty metrics to provide confidence metrics for each classification, enhancing ExoMiner’s first-of-its-kind explainability feature.}
        \resumeItem{Collaborated with NASA engineers to rigorously test and benchmark ExoMiner’s architecture, achieving significant gains in recall and precision over existing exoplanet classifiers.}
        \resumeItem{Research was published in the \textit{Astrophysical Journal}, showcasing ExoMiner’s validation of 301 new exoplanets.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NBA Game Prediction Model} $|$ \emph{Python, PyTorch, scikit-learn, NumPy, Pandas}}{July 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Built an end-to-end data pipeline which scrapes, processes, and analyzes NBA data, enabling efficient feature selection and transformation.}
            \resumeItem{Applied machine learning techniques
            \resumeItem{Automated daily predictions by designing a system that integrates new games, predicts matchups, and processes results, allowing for continuous optimization and iterative improvement.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Personal Bytecode Compiler Project} $|$ \emph{C, Git}}{Sep. 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a multi-pass bytecode compiler, learning from "Crafting Interpreters" and the "Dragon Book" to implement a custom language from scratch.}
            \resumeItem{Designed core components, including a custom garbage collector and symbol table for effective memory management and identifier resolution.}
            \resumeItem{Leveraged recursive parsing and custom-built data structures (e.g., hash tables, dynamic arrays) to optimize just-in-time execution.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------HONORS/AWARDS---------------
\section{Honors}
    \resumeSubHeadingListStart
    \resumeSubheading
    {USA Computing Olympiad (USACO) Platinum Division Qualifier}{Feb. 2023}
    {Ranked in the top 150 competitors in the nations most elite high school competitive programming competition.}{}
%    \resumeSubheading
%    {United States Presidential Scholar Candidate}{April 2023}
%    {Recognized by the Dep.of Education as one of 5,000 of the nation’s "most distinguished high school seniors".}{}
    \resumeSubheading
    {3rd Place, Varsity Public Forum – Indiana State Debate Tournament (ISSDA)}{March 2022}
    {Placed 3rd at Indiana’s statewide debate meet, demonstrating high-level rhetoric and communication skills.}{}
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Java, Python, Bash, JavaScript, TypeScript, OCaml, R} \\
     \textbf{Developer Tools}{: Git, GitHub, UNIX, Docker, VS Code, Cloudfare, PyCharm, IntelliJ, LaTeX, Tpyst} \\
     \textbf{Libraries}{: pandas, NumPy, tensorflow, keras, PyTorch, scikit-learn, tensorflow, seaborn, Matplotlib, OpenGL}
    }
 \end{itemize}


%-------------------------------------------
\end{document}
